---
output:
  reprex::reprex_document:
    venue: "gh"
    advertise: FALSE
    session_info: TRUE
    style: TRUE
    comment: "#;-)"
    tidyverse_quiet: FALSE
    std_out_err: TRUE
knit: reprex::reprex_render
---

```{r}
library("pdfetch") # To obtain data from St. Louis FED
library("xts") # Extended time series
library("reshape2") # To reshape data sets
library("ggplot2") # For plotting
library("ggthemes") # Plot themes
library("plotly")
library("splines")
library("mgcv")
library("YieldCurve")
library("tidyverse")
library("dplyr")
library("splines2")
library("nlme")
```


```{r }
# Load the dataset
data <- read.csv("spotSample.csv")
data <- read.csv("C://Users//xmx13//Desktop//PSTAT 296A//spotSample.csv")

# Format of start date and end date
data$Maturity <- as.numeric(as.Date(as.character(data$MATUR_DATE), form at="%Y%m%d") - 
                            as.Date(as.character(data$START_DT), format="%Y%m%d")) / 365
# Arrange date by order of time to maturity
data <- data %>% 
mutate(Maturity = as.numeric(as.Date(as.character(MATUR_DATE), format="%Y%m%d") - 
as.Date(as.character(START_DT), format="%Y%m%d")) / 365) %>%
arrange(Maturity) 

# Plot the data by start date, which ends up with a nested list
date_list <- data %>%
  group_by(START_DT) %>%
  group_split() %>%
  lapply(function(sub_tibble) {
    sub_tibble %>% distinct() %>% arrange(Maturity) 
  }) 
  

```





```{r }
# Fit and plot the fitted nelson siegel model
fit_nelson_siegel <- function(one_date_list, lambda) {
  
  maturities <- as.numeric(one_date_list$Maturity)
  yields <- as.numeric(one_date_list$ZERO_YLD1)
  
 
  term1 <- 1
  term2 <- (1 - exp(-maturities*lambda)) / (maturities*lambda)
  term3 <- ((1 - exp(-maturities*lambda)) / (maturities*lambda)) - exp(-maturities*lambda)

  new_X <- as.matrix(cbind( term1 = term1, term2 = term2, term3 = term3))
  
  betas <- solve(t(new_X) %*% (new_X)) %*% t(new_X) %*% yields
  print(betas)


  fitted_yields <- new_X %*% betas 
  cov_matrix <- ((yields - fitted_yields) %*% t(yields - fitted_yields))/length(yields)

  return(cov_matrix)
  plot(maturities, yields, main = paste("Fitting Nelson-Siegel Yield Curve", one_date_list$START_DT[1]), type = "o",
       xlab = "Maturities", ylab = "Yields")
  lines(maturities, fitted_yields, col = 2)

  return(cov_matrix)
}

fit_nelson_siegel(date_list[[30]], 0.27)




```
                     



Compute the Basis function using the Cox-deBoor Algorithm.
This function was copied from the CRAN document
https://cran.r-project.org/web/packages/crs/vignettes/spline_primer.pdf
I did my own implementation of this function but it is not as nice.

This is just an implementation of the Cox-deBoor recursion

```{r}
basis <- function(x, degree, i, knots){
  if(degree == 0){
    B <- ifelse((x>=knots[i])&(x<knots[i+1]),1,0)
  } else {
    if((knots[degree + i] - knots[i]) == 0){
      alpha1 <- 0
    } else {
      alpha1 <- (x-knots[i])/(knots[degree+i] - knots[i])
    }
    if((knots[i+degree+1] - knots[i+1]) == 0){
      alpha2 <- 0
    } else {
      alpha2 <- (knots[i+degree+1] - x) / (knots[i+degree+1] - knots[i+1])
    }
    B <- alpha1 * basis(x, (degree-1), i, knots) + 
      alpha2*basis(x, (degree-1), (i+1), knots)
  }
  return(B)
}
```

Construct the matrix $\mathbf{B}$, column by column.
Matrix $B$ contains the basis functions computed through the Cox-deBoor recursive formulas using the function defined in the codechunk above, evaluated at different times to maturity (rows) and at different knot intervals (columns). For more details, check FURM on canvas

```{r}
matrix_b <- function(x, degree=3, int_knots) { 
  # the x argument takes in a vector of time values that 
  # will be used to evaluate a design matrix of basis functions 
  # the degree argument specifies the highest degree of polynomials for
  # the basis functions
  # the int_knots argument takes in a vector of knots that will be used 
  # to determine the intervals of the piecewise function
  bound_knots <- int_knots[c(1, length(int_knots))] # this line creates bound knots
  knots <- c(rep(bound_knots[1], (degree+1)), int_knots[c(-1, -length(int_knots))], rep(bound_knots[2], (degree+1)))
  # the line above adds a couple of extra knots to each end of the int_knots vector because of the Cox-deBoor recursion
  K <- length(int_knots) + degree - 1 # number of columns in the Basis matrix
  B.mat <- matrix(0,nrow = length(x), ncol = K) # initialize the matrix
  for(j in 1:K) {
    B.mat[,j] <- basis(x, degree, j, knots) # add each column, one by one
  }
  return(B.mat) # return the matrix
}
```

test the functions on the yield rates provided by Avery
basically, minimize:

$$
\text{MSE}(\alpha|\mathbf{B}, r) = (r - \mathbf{B}\alpha)^T(r-\mathbf{B}\alpha)
$$
Using OLS (unpenalized)

$$
\alpha = (\mathbf{B}^T\mathbf{B})^{-1} \mathbf{B}^T r
$$
where $r$ is a vector of yield rates



```{r}
# splines for 20 years, evenly spaced date
spline_20_years <- function(spotSample_ordered){
  yields <- spotSample_ordered$ZERO_YLD1
  maturities <- as.numeric(spotSample_ordered$Maturity)
  n <- 26 # number of maturity dates
  x <- as.numeric(spotSample_ordered$Maturity) # maturity dates
  B <- matrix_b(x, degree=3, int_knots = as.vector(quantile(maturities, probs = seq(0,1,.2)))) 
  
  # B is the design matrix on which the least squares coefficients will be calculated
  
  alphas <- solve(t(B) %*% B) %*% t(B) %*% yields # OLS Formula for coefficients
  
  x2 <- seq(1/12, 30, .1) # this range is used to simulate a continuous yield curve
  B2 <- matrix_b(x2, degree =3, int_knots = as.vector(quantile(maturities, probs = seq(0,1,.2)))) 
  # B2 is the matrix of basis functions but evaluated at a 'continuous' time (not really but close enough)
  
  bootstrapped_yields <- data.frame(ttm = x2, yield = B2 %*% alphas) # create dataframes for plotting
  og_yields <- data.frame(ttm = maturities, yield = yields)
  

  sampled_data <- bootstrapped_yields %>%
  slice(seq(1, n(), by = 10)) %>%  # Take every 10th row from the dataset
  rename("Maturity" = ttm, "ZERO_YLD1" = yield) %>% slice(1:30)
  return(sampled_data[2:21,])

}

```






```{r}
# Fit the models by days using spline, then use the bootstrapped date to fit the NS model
spline_20_years(date_list[[12]])
date_list[[12]]
spline_data <- lapply(date_list, spline_20_years)

lambda <- 0.27

cov_data <- lapply(spline_data, function(data) fit_nelson_siegel(data, lambda))
avg_cov <- Reduce("+", cov_data) / length(cov_data)
avg_cov


```




```{r}
# this nelson siegel fit will return the covariance matrix
fit_nelson_siegel <- function(one_date_list, lambda, avg_cov ){
  
  maturities <- as.numeric(one_date_list$Maturity)
  yields <- as.numeric(one_date_list$ZERO_YLD1)
  

  term1 <- 1
  term2 <- (1 - exp(-maturities*lambda)) / (maturities*lambda)
  term3 <- ((1 - exp(-maturities*lambda)) / (maturities*lambda)) - exp(-maturities*lambda)
  
  new_X <- as.matrix(cbind( term1 = term1, term2 = term2, term3 = term3))
  

  if(!is.null(avg_cov)){ #GLS (if we have a covariance input)
    # transform GLS to OLS
    avg_cov <- avg_cov + diag(20)*10^(-10)  
    L <- t(chol(avg_cov))
    new_yields <- solve(L) %*% yields
    new_X <- solve(L) %*% new_X 
  }

  
  betas <- solve(t(new_X) %*% (new_X)) %*% t(new_X) %*% yields # compute the beta from OLS( transformed GLS)
  #print(betas)


  fitted_yields <- new_X %*% betas 
  cov_matrix <- ((yields - fitted_yields) %*% t(yields - fitted_yields))
  
  return(cov_matrix)

}

```


```{r }
# GLS
grid <- seq(0.03, 0.3, 0.03)
cov_matrix_covergence <- matrix(0,10,20)
h <- 1

for(lambda in grid){ # search the lambda values by grid 
  avg_cov <- NULL
  k <- 1
  prev <- matrix(0,20,20)
  while((k <= 20)){ # condition for convergence
    cov_data <- lapply(spline_data, function(data) fit_nelson_siegel(data, lambda, avg_cov)) # compute the covariance matrix for each day
    avg_cov <- Reduce("+", cov_data) / length(cov_data) # compute the average covariance matrix for 30 days

    cov_matrix_covergence[h,k] <- sqrt(abs(sum(as.vector(avg_cov) - as.vector(prev)))) # compare the difference with the previous iteration 
    prev <- avg_cov # previous iteration average covariance matrix

    k = k+1
  }

  h <- h+1
}

cov_matrix_covergence[]
```





```{r}
lambda <- 0.27

maturities <- as.vector(spline_data[[1]]$Maturity)
yields <- as.vector(spline_data[[1]]$ZERO_YLD1)

term+1 <- 1
term2 <- (1 - exp(-maturities*lambda)) / (maturities*lambda)
term3 <- ((1 - exp(-maturities*lambda)) / (maturities*lambda)) - exp(-maturities*lambda)

matrix_result <- as.matrix(cbind( term1 = term1, term2 = term2, term3 = term3))
matrix_result



avg_cov <- avg_cov + diag(20)*10^(-10)  

L <- t(chol(avg_cov))
new_yields <- solve(L) %*% yields
new_X <- solve(L) %*% matrix_result
solve(L) %*% L
beta_s <- solve(t(new_X) %*% (new_X)) %*% t(new_X) %*% new_yields
beta_s


```

```{r}


```